---
title: "Get started"
author: '<h4>Authors: <i>`r auths <- eval(parse(text = gsub("person","c",read.dcf("../DESCRIPTION",
  fields = "Authors@R"))));paste(auths[names(auths)=="given"],auths[names(auths)=="family"],
  collapse = ", ")`</i></h4>'
date: '<h4>Vignette updated: <i>`r format( Sys.Date(), "%b-%d-%Y")`</i></h4>'
output: BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{echoverseTemplate}
   %\usepackage[utf8]{inputenc}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, echo=FALSE, include=FALSE}
pkg <- read.dcf("../DESCRIPTION", fields = "Package")[1]
```

# Introduction

`echoverseTemplate` is a skeleton R package that serves as a starting point
for creating new modules within the
[echoverse](https://github.com/RajLabMSSM/echoverse) suite of
genomic fine-mapping tools.

It provides:

- A ready-made package structure following Bioconductor conventions.
- Internal utility functions (`messager`, `stopper`, `message_parallel`)
  for consistent messaging across echoverse modules.
- Pre-configured CI/CD via
  [rworkflows](https://github.com/neurogenomics/rworkflows).

# Usage

To create a new echoverse module from this template:

1. Copy or fork the repository.
2. Rename the package (update `DESCRIPTION`, `NAMESPACE`, vignettes, etc.).
3. Add your exported functions under `R/`.
4. Document with `roxygen2` and rebuild the `NAMESPACE`.

# Internal utilities

The package includes three internal helpers shared across echoverse modules:

- **`messager()`** -- Conditionally print messages, with support for
  parallel contexts.
- **`stopper()`** -- Conditionally raise stop errors.
- **`message_parallel()`** -- Send messages to the console from within
  parallel processes.

# Session Info

<details>

```{r Session Info}
utils::sessionInfo()
```

</details>

<br>
