---
title: "echolocatoR Fine-mapping Portal" 
author: "<h4>Author: <i>Brian M. Schilder</i></h4>" 
date: "<h4>Most recent update: <i>`r format( Sys.Date(), '%b-%d-%Y')`</i></h4>"
output:
  BiocStyle::html_document:
    self_contained: yes
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: show
    df_print: paged
vignette: >
    %\VignetteIndexEntry{echolocatoR_Finemapping_Portal} 
    %\usepackage[utf8]{inputenc}
    %\VignetteEngine{knitr::rmarkdown} 
editor_options: 
  markdown: 
    wrap: 72
---

```{r style, echo=FALSE, results='asis', message=FALSE}
BiocStyle::markdown()
knitr::opts_chunk$set(tidy = FALSE,
                      message = FALSE)
```

```{r setup}
library(echodata)
```

The *echolocatoR.

The following functions provides API access to the fine-mapping results, 
pre-computed LD matrices, and plots available on the [**echolocatoR Fine-mapping Portal**](https://rajlab.shinyapps.io/Fine_Mapping_Shiny/).

# View metadata

Peruse the metadata to see the available 
data types (e.g. "GWAS", "QTL"), 
datasets (e.g. "Ripke_2014", "Wray_2018"), and 
phenotypes (e.g. "Schizophrenia", "Major Depressive Disorder").

```{r}
meta <- echodata::portal_metadata()
knitr::kable(meta)
```
# Query portal

Query and download data from the [**echolocatoR Fine-mapping Portal**](https://rajlab.shinyapps.io/Fine_Mapping_Shiny/).

`portal_query` will return a list of paths where each file 
has been downloaded locally, in a hierarchical folder structure 
(i.e. `dataset_type --> dataset --> locus --> data_types` )

```{r}
local_finemap <- echodata::portal_query(dataset_types="GWAS",
                                        phenotypes = c("schizophrenia",
                                                       "parkinson"),
                                        file_types = "multi_finemap",
                                        loci = c("BST1","CHRNB1","LRRK2"),
                                        LD_panels = "1KGphase3")
```

# Session Info 

<details> 

```{r Session Info}
utils::sessionInfo()
```

</details>  

